Language-Based Security for Low-Level MPC

### 2024-05-13 ppdp24/examples.tex
checkpoint

\paragraph{Oblivious Transfer} \cnote{Here is where we
  wave hands about OT.}

$$
\OT{\elab{\be_1}{\cid}}{\be_2}{\be_3}
$$
$$
\begin{array}{l}
\solve{\stores}{\OT{\elab{\be_1}{\cid_1}}{\be_2}{\be_3}}{\cid_2} = \\
\qquad ((\solve{\stores}{\be_1}{\cid_1}) \cap 
(\solve{\stores}{\be_2}{\cid_2})) \cup \\
\qquad ((\stores - (\solve{\stores}{\be_1}{\cid_1})) \cap
(\solve{\stores}{\be_3}{\cid_2})
\end{array}
$$

@@

Eliminating cheating by adding information theoretic secure MAC codes
to shares is a fundamental approach realized by protocols such as BDOZ
\cite{XXX} and SPDZ \cite{XXX}.  These protocols assume a
pre-processing phase that distributes shares with MAC codes to
clients.  This integrates well with pre-processed Beaver Triples to
implement malicious secure, and relatively efficient, multiplication
\cite{XXX}.  Here we show how to implement malicious secure two party
multiplication in the BDOZ style via some extensions of $\minifed$.

>>>>

\paragraph{Oblivious Transfer} A passive secure OT protocol
based on previous work \cite{XXX} can be defined in $\metaprot$,
however this protocol assumes some shared randomness. Alternatively,
a simple passive secure OT can be defined with the addition of
public key cryptography as a primitive. But given the diversity
of approaches to OT, we instead assume that OT is abstract with
respect to its implementation, where calls to OT in $\mathbb{F}_2$
are of the following form-- given a \emph{choice bit}
$\be_1$ provided by a receiver $\cid$, the sender
sends either $\be_2$ or $\be_3$.
$$
\OT{\elab{\be_1}{\cid}}{\be_2}{\be_3}
$$
Critically, the sender learns nothing about $\be_1$ and the
receiver learns nothing about the unselected value, so we interpret
these calls in our implementation in $\mathbb{F}_2$ as follows.
$$
\begin{array}{l}
\solve{\stores}{\OT{\elab{\be_1}{\cid_1}}{\be_2}{\be_3}}{\cid_2} = \\
\qquad ((\solve{\stores}{\be_1}{\cid_1}) \cap 
(\solve{\stores}{\be_2}{\cid_2})) \cup \\
\qquad ((\stores - (\solve{\stores}{\be_1}{\cid_1})) \cap
(\solve{\stores}{\be_3}{\cid_2})
\end{array}
$$

@@

In a malicious setting, detecting cheating by adding
information-theoretic secure MAC codes to shares is a fundamental approach
realized by protocols such as BDOZ \cite{XXX} and SPDZ \cite{XXX}.
These protocols assume a pre-processing phase that distributes shares
with MAC codes to clients.  This integrates well with pre-processed
Beaver Triples to implement malicious secure, and relatively
efficient, multiplication \cite{XXX}.  Here we show how to implement
malicious secure two party multiplication in the BDOZ style in
$\metaprot$.
